Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
cleanup

	Then, we join the pivot node to a~larger ground set to force its eviction.
	Precisely,
	we create a~ground set $\{x_0, y_0\}$, 	where
%	 $x_0$ is the current pivot node and
	 $y_0$ is an arbitrary isolated node.
	Since \ALG does not have $\{x_0,y_0\}$ collocated, 
	the adversary issues external requests to this pair until \ALG collocates it.
	\ALG cannot collocate $\{x_0, y_0\}$ with $B$ (as $B$'s size is $k-1$), hence it collocates them in a~different cluster.
	In order to preserve a~feasible partition of nodes after collocating $\{x_0, y_0\}$,
	\ALG must replace $x_0$ with another isolated node that becomes the new pivot.
%	denoted by $x_1$.

	We proceed by joining the current pivot node to a~larger ground set in  similar steps.
	Consider the step $i$,
	when the isolated node $x_i$ is collocated with $B$.
	 We issue a request between $x_i$ and some node $y_i \in C_i$,
	 where $C_i$ is the largest ground set
	 s.t.~$I(C_i) = I(x_i), C_i \neq \{x_0,y_0\}$.
%	 only if  a feasible partition exists
%	 that collocates all nodes in $\{x_i\} \cup C_i $.
	Any feasible partition replaces $x_i$ with some isolated node $x_{i+1}$,
	as the new ground set $\{x_i\} \cup C_i $  may not be ever split.
%	Otherwise,
%	no such feasible partition exists and
%	we terminate the process.
	We terminate the process once the number of remaining isolated nodes 
	is less than $\ell+3$.
	At each step $i$,
	the number of isolated nodes decrease by one or two.
	Then, once the process terminates,
	there are at least $\ell+1$ isolated nodes left.

	  Next, we argue that a partition exists when the process terminates.
	 This implies that a feasible partition exists after any earlier step as well.
%	 Assume for contradiction that the partition is not feasible.	 
	 Since there are at least $\ell+1$ isolated nodes left,
	 there must be two isolated nodes $x^*$ and $y^*$,
	  with the same cluster of origin,
	 i.e., $I(\{x^*\}) = I(\{y^*\})$.
	 Consider the partition $P^*$
	  obtained from the initial partition after swapping $x_0$ and $y_0$
	 with $u$ and $v$ (respectively).
	 In this partition,
	 the ground set $\{x_0,y_0\}$ is collocated in the cluster $I(\{x^*,y^*\})$.
	 Note that after the first request $\{x_0,y_0\}$,
	   we issue requests only between nodes that have the same cluster of origin and
	   all these nodes are collocated in $P^*$.
	 Therefore all ground sets constructed so far are collocated in  $P^*$,
	 i.e., $P^*$ is a feasible partition.
%	 Hence, there are at most $\ell$ isolated nodes after the termination.

>>>>

	Then, we join the pivot node to a~larger ground set to force its eviction.
	Precisely,
	we create a~ground set $\{x_0, y_0\}$, 	where
%	 $x_0$ is the current pivot node and
	 $y_0$ is an arbitrary isolated node.
	Since \ALG does not have $\{x_0,y_0\}$ collocated, 
	the adversary issues an external request to this pair so that \ALG collocates it.
	\ALG cannot collocate $\{x_0, y_0\}$ with $B$ (as $B$'s size is $k-1$), hence it collocates them in a~different cluster.
	In order to preserve a~feasible partition of nodes after collocating $\{x_0, y_0\}$,
	\ALG must replace $x_0$ with another isolated node that becomes the new pivot.
%	denoted by $x_1$.

	We proceed in similar steps by joining the current pivot node to a ground set of the same origin residing in a different cluster.
	Consider the step $i$,
	when the isolated node $x_i$ is collocated with $B$.
	 We issue a request between $x_i$ and some node in $C_i$,
	 where $C_i$ is the largest ground set
	 s.t.~$I(C_i) = I(x_i), C_i \neq \{x_0,y_0\}$.
%	 only if  a feasible partition exists
%	 that collocates all nodes in $\{x_i\} \cup C_i $.
	Any feasible partition replaces $x_i$ with some isolated node $x_{i+1}$,
	as the new ground set $\{x_i\} \cup C_i $  may not be ever split.
%	Otherwise,
%	no such feasible partition exists and
%	we terminate the process.
	We terminate the process once the number of remaining isolated nodes 
	is less than $\ell+3$.
	At each step $i$,
	the number of isolated nodes decrease by one or two.
	Therefore, once the process terminates,
	there are at least $\ell+1$ isolated nodes left.

	  Next, we argue that a partition exists when the process terminates.
	 This implies that a feasible partition exists after any earlier step as well.
%	 Assume for contradiction that the partition is not feasible.	 
	 Since there are at least $\ell+1$ isolated nodes left,
	 there must be two isolated nodes $x^*$ and $y^*$,
	  with the same cluster of origin,
	 i.e., $I(\{x^*\}) = I(\{y^*\})$.
	 Consider the partition $P^*$
	  obtained from the initial partition after swapping $x_0$ and $y_0$
	 with $x^*$ and $y^*$ (respectively).
	 In this partition,
	 the ground set $\{x_0,y_0\}$ is collocated in the cluster $I(\{x^*,y^*\})$.
	 Note that after the first request $\{x_0,y_0\}$,
	   we issue requests only between nodes that have the same cluster of origin and
	   all these nodes are collocated in $P^*$.
	 Therefore all ground sets constructed so far are collocated in  $P^*$,
	 i.e., $P^*$ is a feasible partition.
%	 Hence, there are at most $\ell$ isolated nodes after the termination.
